---
title: "MIS 64018 - Assignment 6"
author: "Ryan Harris"
date: "11/7/2021"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Load library

```{r}
library(lpSolveAPI)
```

Load the .lp file which was created in R by hand (no coding)

```{r}
x <- read.lp("rharri74_6.lp") # create an lp object x
x                          # display x
```

Solve the lp model
```{r}
solve(x)
```

```{r}
get.objective(x)
```

```{r}
get.variables(x)
```

Question 2:

x~1~: 0

x~2~: 0

x~3~: 0

y~1~^+^: 50

y~1~^-^: 0

y~2~^-^: 75

Question 3:

The model above does not work because it suggests x~1~, x~2~, and x~3~ = 0. Thus it is showing the full penalty for both y~1~ and y~2~. This may be because I was unable to enter a constraint to maximize P. The example in the presentation showed constrains with bounds and I was unable to locate anything online or in the reading to specify how to enter the maximize function in R.