---
title: "MIS 64018 - Assignment 5"
author: "Ryan Harris"
date: "10/31/2021"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)
```

Load libraries

```{r}
library(lpSolveAPI)
library(Benchmarking)
```


Create Matrix

```{r}
x <- matrix(c(150,400,320,520,350,320,0.2,0.7,1.2,2.0,1.2,0.7),ncol = 2)
y <- matrix(c(14000,14000,42000,28000,19000,14000,3500,21000,10500,42000,25000,15000),ncol = 2)
colnames(y) <- c("reimbursed_patient-days","privately_paid_patient-days")
colnames(x) <- c("staff_hours_per_day","supplies_per_day")
x
y
```
## DEA Assumptions {.tabset}

### FDH
```{r}
e <- dea(x,y,RTS = "fdh")            # provide the input and output 
eff(e)                               # display efficiencies
peers(e)                             # identify the peers
lambda(e)                            # identify the relative weights given to the peers
```

Free Disposability Hull shows all facilities as efficient.

### CRS
```{r}
e <- dea(x,y,RTS = "crs")            # provide the input and output 
eff(e)                               # display efficiencies
peers(e)                             # identify the peers
lambda(e)                            # identify the relative weights given to the peers
```

Constant Return to Scale (CRS) shows Facilities 1-4 as efficient. Facility 5 has a 97.8% efficiency and Facility 6 has an 86.8% efficiency. Both had Facilities 2 and 4 as peers. 

### VRS
```{r}
e <- dea(x,y,RTS = "vrs")            # provide the input and output 
eff(e)                               # display efficiencies
peers(e)                             # identify the peers
lambda(e)                            # identify the relative weights given to the peers
```

Varying Return to Scale (VRS) shows Facilities 1-5 as efficient. Facility 6 has a 89.6% efficiency with Facilities 2 and 5 as peers.

### IRS
```{r}
e <- dea(x,y,RTS = "irs")            # provide the input and output 
eff(e)                               # display efficiencies
peers(e)                             # identify the peers
lambda(e)                            # identify the relative weights given to the peers
```

Increasing Return to Scale (IRS) shows Facilities 1-5 as efficient. Facility 6 has a 89.6% efficiency with Facilities 2 and 5 as peers. This is the same result as VRS.

### DRS
```{r}
e <- dea(x,y,RTS = "drs")            # provide the input and output 
eff(e)                               # display efficiencies
peers(e)                             # identify the peers
lambda(e)                            # identify the relative weights given to the peers
```

Decreasing Return to Scale (DRS) shows Facilities 1-4 as efficient. Facility 5 has a 97.8% efficiency and Facility 6 has an 86.8% efficiency. Both had Facilities 2 and 4 as peers. This is the same result as CRS.

### FRH
```{r}
e <- dea(x,y,RTS = "add")            # provide the input and output 
eff(e)                               # display efficiencies
peers(e)                             # identify the peers
lambda(e)                            # identify the relative weights given to the peers
```
Free Replacibility Hull shows all facilities as efficient.

## Compare and Contrast
The results were showed three different results, in the following pairs:

<ul>
<li><b>FDH and FRH</b>
<ul><li>All six facilities are efficient</li>
</ul></li>
<li><b>VRS and IRS</b>
<ul><li>Facilities 1-5 are efficient</li>
<li>Facility 6 has an 89.6% efficiency</li>
<li>Facility 6 has Facilities 2 and 5 as peers</li>
</ul></li>
<li><b>DRS and CRS</b>
<ul><li>Facilities 1-4 are efficient</li>
<li>Facility 5 has an 97.8% efficiency and Facility 6 has an 86.8% efficiency</li>
<li>Facilities 5 and 6 have Facilities 2 and 4 as peers</li>
</ul></li>
</ul>
